Proof No Diamond (3 layers)

### 2025-12-11 CAV2026B_cart_pole/CAV2026_a_proof.tex

\begin{theorem}
	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe, then
	there exists a DT certificate for safety. 
\end{theorem}

@@

The proof is in three steps: \begin{itemize}
	\item First, we will show, $R(I)$ has an open neighborhood contained in $R_\delta(I)$ and hence disjoint with $U$.

	\item Second, we will show $R(I)$ is attractive in a neighborhood. 
\end{itemize}

@@

\begin{proof}
	Trivial.
\end{proof}

@@

\begin{proof}
	In this proof, we use $R_i$ to denote each $R_{\delta/2}(I)\cap Q_i$. We need to show $R_{\delta/2}(I)$ is attractive in $\bigcup_{i\in I}B_\varepsilon(R_i)\cap Q_i$.

	By assumption and definition, each $Q_i$ is assigned with a Lipschitz continuous function $f_i$ with Lipschitz constant $K_i$. Let $K = \max_{i\in I} K_i$ and $\varepsilon = \frac{\delta}{2K+1}$.

	For a point $y$ in $B_\varepsilon(R_i)\cap Q_i$, there exists $x\in R_i$ such that $d(x,y)<\varepsilon$. We consider $succ_p(y)$ and $succ_p(x)$.

	Since $x,y\in Q_i$, $d(p(x),p(y))\leq K_i d(x,y) < K \varepsilon<\delta/2$. Because $x\in R_i\subseteq R_{\delta/2}(I)$, by definition, since $succ_p(y)\in B_{K_i\varepsilon}(succ_p(x))$ and $x\in R_{\delta/2}(I)$, then $succ_p(y)\in R_{\delta/2}(I)$.

>>>>

\begin{theorem}
	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe and $succ$ of the system is Lipschitz continuous, then
	there exists a DT certificate for safety.

	Here, a set value function $f$ is Lipschitz if there exists a constant $C$ such that for any $x,y$ with $d(x,y)=d$, $f(y)\subseteq B_{Cd}(f(x))$.
\end{theorem}

@@

 Without loss of generality, we assume the Lipschitz constant for $succ$ is 1.

The proof is in several steps: \begin{itemize}
	\item First, we will show, $R_{\delta/2}(I)$ has an open neighborhood contained in $R_\delta(I)$ and hence disjoint with $U$.

	\item Second, we will show $R_{\delta/2}(I)$ is attractive in a neighborhood. 
\end{itemize}

@@

\begin{proof}
  This is by definition.
\end{proof}

@@

\begin{proof}
	We use $R_i$ to denote each $R_{\delta/2}(I)\cap Q_i$.	By assumption, each $Q_i$ is assigned with a Lipschitz continuous function $f_i$ with Lipschitz constant $K_i$. Let $K = \max_{i\in I} K_i$ and $\varepsilon = \frac{\delta}{2K+2} < \delta/2$ (for $L_\infty$ distance; for other distance as $L_2$, $L_1$, $\varepsilon$ should be smaller).

	For a point $y$ in $B_\varepsilon(R_i)\cap Q_i$, there exists $x\in R_i\subseteq Q_i$ such that $d(x,y)<\varepsilon$. We consider $succ_p(y)$ and $succ_p(x)$.

	Since $x,y\in Q_i$, $d(p(x),p(y))\leq K_i d(x,y) < K \varepsilon<\delta/2$.  By assumptions, we have $succ_p(y)\subseteq B_{\delta/2}(succ_p(x))$. Because $x\in R_i\subseteq R_{\delta/2}(I)$, by definition, we have that $succ_p(y)\subseteq R_{\delta/2}(I)$.
